Papers

### 2023-12-11 papers.qmd
add slides

## Invited Talks
"Elasic Bayesian Model Calibration" *FSU Shape Group Statistical Meeting*, January 24, 2023, [Slides](https://jdtuck.github.io/presentations/FSU_Jan23/FSU_Jan23.html)

>>>>

## Invited Talks
"Elasic Bayesian Model Calibration" *ASA SDNS Webinar*, December 04, 2023, [Slides](https://jdtuck.github.io/ASA_23_Calibration/index.html)

"Elasic Bayesian Model Calibration" *FSU Shape Group Statistical Meeting*, January 24, 2023, [Slides](https://jdtuck.github.io/presentations/FSU_Jan23/FSU_Jan23.html)
